Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-10 mtjournal.tex
incorporated Mari's draft abstract

\begin{abstract}
Abstract to go here
\end{abstract}
\keywords{machine translation evaluation, syntax, dependency trees}

@@

>>>>

\begin{abstract}
  Recent efforts aimed at improving over standard machine translation
  evaluation methods (BLEU, TER) have investigated mechanisms for
  accounting for allowable wording differences either in terms of
  syntactic structure or synonyms/paraphrases. This paper explores an
  approach for combining scores from partial syntactic dependency
  matches with standard local n-gram matches using a statistical
  parser, and taking advantage of parse probabilities in deriving
  expected scores based on the N-best parses for the hypothesized
  sentence translation.  The new scoring metric, Expected Dependency
  Pair Match (EDPM), is shown to be superior to BLEU and TER in terms
  of correlation to human judgements and as a per-document and
  per-sentence predictor of HTER, using mean subtraction to account
  for document difficulty. Further, we explore the potential benefit
  of combining the n-gram and syntactic features of EDPM with the
  alternative wording features of TERp, with experiments showing that
  there is a benefit to accounting for syntactic structure on top of
  the semantic equivalency features.
\end{abstract}
\keywords{machine translation evaluation, syntax, dependency trees}

@@

\subsection{HTER corpus}
